Taking Dyads Seriously

### 2018-02-05 paper/4_app.tex
small edit to top of app

We choose five prominent studies from the broad field of international relations and international political economy that utilize relational data \citep{reiter:stam:2003, mcdonald:2004,  rose:2004, weeks:2012, gibler:2017}. These articles demonstrate the broad range of application for the AME framework, which include testing the effect of both dyadic and monadic variables on varied conflict behaviors and trade. It is worth noting, however, that the AME is applicable only where a full set of dyads for an outcome of interest is observable. The AME is not applicable to analyses of case-level data, for example, studies that examine the decision to go to war by particular states (e.g., the USA).

These studies were also selected to be recent and prominent (cited over 100 times). Each of these pieces was published in a prominent journal and is well-known in the literature. Each used the standard approach in political science, which is to employ some form of a general linearized regression that ignores dyadic interdependencies, except as they may reveal themselves in included variables. In addition, most of these studies adjust the standard errors in an attempt to account for the clustering of observations. We follow the strategy of the original study in our re-estimation of the original models.

>>>>

We choose five recent studies from the broad field of international relations and international political economy that utilize relational data \citep{reiter:stam:2003, mcdonald:2004,  rose:2004, weeks:2012, gibler:2017}. These articles demonstrate the broad range of application for the AME framework, which include testing the effect of both dyadic and monadic variables on varied conflict behaviors and trade. It is worth noting, however, that the AME is applicable only where a full set of dyads for an outcome of interest is observable  -- for example it is unsuitable for studying onsets, where dyad-years representing conflict continuations are removed from the sample. The AME is not applicable to analyses of case-level data, for example, studies that examine the decision to go to war by particular states (e.g., the USA).

These studies were also selected based on how recent they were and whether they had more then 100 citations. Each of these pieces was published in a prominent journal and is well-known in the literature. Each used the standard approach in political science, which is to employ some form of a general linearized regression that ignores dyadic interdependencies, except as they may reveal themselves in included variables. In addition, most of these studies adjust the standard errors in an attempt to account for the clustering of observations. We follow the strategy of the original study in our re-estimation of the original models.
